%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[colorlinks = true, linkcolor = MidnightBlue, urlcolor  = MidnightBlue, citecolor = MidnightBlue, anchorcolor = MidnightBlue]{hyperref}

%----------------------------------------------------------------------------------------
%	HEADER SECTION
%----------------------------------------------------------------------------------------

\name{Ankit Chouhan} % Your name
\address{Hostel 2, MANIT, Bhopal - 462003}
\address{\href{mailto:ankitchouhan1020@gmail.com}{ankitchouhan1020@gmail.com}~$\cdot$~github: \href{http://github.com/ankitchouhan1020}{@ankitchouhan1020}~$\cdot$~(+91) 9630938548}

\begin{document}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Maulana Azad National Institute Of Technology, Bhopal} \hfill {\em May 2016 - Present} 
\\ \textbf{B.Tech.} - Computer Science And Engineering \hfill{CGPA: 7.878}
\\
\\{\bf Govt. Higher Secondary School, Rehti, Dist. Sehore} \hfill {\em 2014 - 2015} 
\\ $12^{th}$\hfill {Percentage: 97.2 }
\\
\\{\bf New Model Higher Secondary School, Rehti, Dist. Sehore} \hfill {\em 2012 - 2013} 
\\ $10^{th}$\hfill {Percentage: 91.3}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL SSKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages:\ & HTML5, CSS/SCSS, Javascript, Python, C/C++
\\
Frameworks:\ & VueJS
\\
General:\ & Data Structures, Algorithms, Material Design
\\
Others:\ & Operating System, DBMS
\\
\end{tabular}

\end{rSection}
%--------------------------------------------------------------------------------
%    Projects SECTION
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
{\bf Conduit : Publishing Platform}
\\
Medium is an online publishing platform. This is similar to Medium. In this project, I have developed frontend of this website.
https://github.com/ankitchouhan1020/medium-clone\\
 {\scriptsize Technologies used: VueJS 2}
\\
{\bf GSoC-Orgs-with-Technologies-List}
\\
Python script to get participated GSoC organisations 2018 list with their working technologies.\\
https://github.com/ankitchouhan1020/GSoC-Orgs-with-Technologies-List
\\
 {\scriptsize Technologies used: Python3, Beautiful Soup}
\\
{\bf Eureka Web App}\\
Eureka is an online event organised by Vision. It's a five-day long online event. Each day question was
published on the website page and response from the authenticated user was recorded in database.
\\
{\scriptsize Technologies used: Vue JS, Vuetify.}
\\
{\bf Vision Website}\\
Vision is a Technical Society at MANIT Bhopal. A team of three students, including me,
developed this website.
\\
{\scriptsize Technologies used: HTML, CSS, Javascript}
\end{rSection}

%----------------------------------------------------------------------------------------
%	ACADEMIC SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Achievements}
{\bf ICPC Regional Online Round Qualified}
\\
Our team ccoders30 was selected for ACM ICPC 2018 onsite in the Kolkata-Kanpur Regionals
Online Round.
\end{rSection}

%----------------------------------------------------------------------------------------
%	POSITION OF RESPONSIBILITY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Positions of Responsibility}
{\bf Web Administrator Vision}
\\
Organised Eureka 2018 (annual event of vision), created webpage for NOESIS 2018 and maintaining vision website.
\\
{\bf Student Head at Spic Macay MANIT Chapter}
\\
Organised Spic Macay events in various schools and colleges in Bhopal.
\end{rSection}

\end{document}
